Penalized linear mixed models for structured genetic data

### 2021-02-25 main.tex
Updating figures 5, 6

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\caption{Precision recall curves across $\lambda$ values from the Empirical genome-wide analysis. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}

\begin{figure}[hbt]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pc1_corr.png}
\caption{Pathwise absolute correlation of selected, non-causal SNPs with the first principal component of the data in Empirical genome-wide analysis. Plotted line is the mean absolute correlation of all incorrectly selected SNPs for a particular $\lambda$ value, with shaded region for $\pm$ 1 SE. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_pc1_corr}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_prc.png}
\caption{Precision recall curves across $\lambda$ values from the Empirical genome-wide analysis. Single replication case study with $\eta = 0.5, \xi = 0.8$.}
\label{fig:gw_prc}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale = 0.9]{figures/genomewide_pc1_corr.png}
\caption{Pathwise absolute correlation of selected, non-causal SNPs with the first principal component of the data in Empirical genome-wide analysis. Plotted line is the mean absolute correlation of all incorrectly selected SNPs for a particular $\lambda$ value, with shaded region indicating $\pm$ 1 SE. Single replication case study with $\eta = 0.5, \xi = 0.8$. \anna{get rid of 'Method' legend title.}}
\label{fig:gw_pc1_corr}
\end{figure}
